---
title: "Approximation of the Standard Normal Distribution"
author: "Yang Jie"
date: "2020/3/26"
output:
  html_document: default
  word_document: default
  pdf_document: default
fontsize: 11pt
papersize: letter
documentclass: article
---

## Abstract

The Monte Carlo methods are used to calculate the approximate value of the standard normal distribution, and the box plots show the error of the method intuitively.


## Math Equations

The equation for the standard normal distribution $N(0, 1)$ is 

$$
\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2}dy
\tag{1}
$$

The equation for the Monte Carlo methods is

$$
\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t)
\tag{2}
$$
where $X_i$ is a random sample from $N(0, 1)$, $I(\cdot)$ is the indicator function.


## Table


Experiment with the approximation at $n \in \{10^2, 10^3, 10^4\}$ at $t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$ to form a table.
The approximation results are shown in the table.And it includes the true value for comparison.




|          |t=0   |t=0.67|t=0.84|t=1.28|t=1.65|t=2.32|t=2.58|t=3.09|t=3.72|
|---------:|-----:|-----:|-----:|-----:|-----:|-----:|-----:|-----:|-----:|
|     n=100|0.5000|0.8000|0.8300|0.9100|0.9800|1.0000|1.0000|1.0000|1.0000|
|    n=1000|0.5390|0.7460|0.8150|0.9040|0.9420|0.9910|0.9940|0.9990|1.0000|
|   n=10000|0.4911|0.7518|0.7963|0.8986|0.9489|0.9903|0.9946|0.9992|1.0000|
|True Value|0.5000|0.7486|0.7995|0.8997|0.9505|0.9898|0.9951|0.9990|0.9999|



## Figures
Further, repeat the experiment 100 times.Draw box plots of the 100 approximation errors at each $t$ using **ggplot2** for each $n$.Due to limited space, this article only lists the picture named "t=0.67".


```{r,echo=FALSE}
library(ggplot2)
library(lattice)
library(plyr)
library(Rmisc)

t=c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
y=c(0.5000,0.7486,0.7995,0.8997,0.9505,0.9898,0.9951,0.9990,0.9999 )
n=c(100,1000,10000)
total=matrix(0,100,3)

for (j in 1:3) {
 err=rep(0,100)
 for (i in 1:100){
  a=rnorm(n[j],0,1)
  ypre=mean(a<y[2])
  err[i]=ypre-y[2]
  p=data.frame(err)
 }
 total[,j]=err
}

g1=ggplot(p,aes(x="t=0.67", y=total[,1])) +  geom_boxplot() +labs(title="t=0.67,n=100", y = "error")
g2=ggplot(p,aes(x="t=0.67", y=total[,2])) +  geom_boxplot()+labs(title="t=0.67,n=1000", y = "error")
g3=ggplot(p,aes(x="t=0.67", y=total[,3])) +  geom_boxplot()+labs(title="t=0.67,n=10000", y = "error")
g=multiplot(g1,g2,g3)
```



# Code Chunk 
The following code is the  main idea  to draw box plots.

```{r}
#加载包
library(ggplot2)
library(lattice)
library(plyr)
library(Rmisc)

#列出数据，其中y为分别取t值的标准正态分布下的值
t=c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
y=c(0.5000,0.7486,0.7995,0.8997,0.9505,0.9898,0.9951,0.9990,0.9999 )
n=c(100,1000,10000)

#定义一个100行3列的空矩阵
total=matrix(0,100,3)

#循环嵌套
for (j in 1:3) {
 err=rep(0,100)
 for (i in 1:100){
  a=rnorm(n[j],0,1)
  ypre=mean(a<y[2])
  err[i]=ypre-y[2]
  p=data.frame(err)
 }
 total[,j]=err
}

#multiplot函数可用来将多张图片整合成一张输出
#g1=ggplot(p,aes(x="t=0.67", y=total[,1])) +geom_boxplot() +labs(title="t=0.67,n=100", y = "error")
#g2=ggplot(p,aes(x="t=0.67", y=total[,2])) +  geom_boxplot()+labs(title="t=0.67,n=1000", y = "error")
#g3=ggplot(p,aes(x="t=0.67", y=total[,3])) +  geom_boxplot()+labs(title="t=0.67,n=10000", y = "error")
#g=multiplot(g1,g2,g3)
```

## Summary
Get approximation of the distribution function of$N(0, 1)$by the Monte Carlo methods.And there are still some difficulties in programming with R , especially on loop statements. Logic must be clear when programming.